HO unification from object language to meta language

### 2024-02-16 main.tex
wip abstract

The object logic we are interested in is Dependent Type Theory (DTT) for which
want to implement a unification procedure \U{} using
Elpi~\cite{dunchev15lpar}, a dialect of $\lambda$Prolog.
Elpi comes equipped with and equational theory \Ue{} that comprises $\eta\beta$ equivalence
and higher order unification restricted to the pattern
fragment~\cite{miller92jsc}.
We want \U{} to feature the same equational theory of \Ue{}, but on the
object logic DTT. Unfortunately the natural encoding of DTT in Elpi, that we call \Fo{},
``underuses'' \Ue{} by making it applicable to first order unification problems only.
To overcome the problem we provide a better
behaved encoding \Ho{}, we show how to map a unification problems in \Fo{}
to related problems in \Ho{} and
how to map back the unifiers found by \Ue{}, effectively implementing
 \U{} on top of \Ue{} for the natural encoding \Fo{}.

>>>>

The object logic we are interested in is Dependent Type Theory (DTT) for which
want to implement a unification procedure \U{} using
Elpi~\cite{dunchev15lpar}, a dialect of $\lambda$Prolog.
Elpi comes equipped with the equational theory \Ue{} that comprises $\eta\beta$ equivalence
and higher order unification restricted to the pattern
fragment~\cite{miller92jsc}.
We want \U{} to feature the same equational theory of \Ue{}, but on the
object logic DTT. Unfortunately the natural encoding of DTT in Elpi, that we call \Fo{},
``underuses'' \Ue{} by making it applicable to first order unification problems only.
To overcome the problem we provide a better
behaved encoding \Ho{}, we show how to map a unification problems in \Fo{}
to related problems in \Ho{} and
how to map back the unifiers found by \Ue{}, effectively implementing
 \U{} on top of \Ue{} for the natural encoding \Fo{}.
